Capstone Movielens Report

### 2025-12-08 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: calc_day_general_effect.

This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below).
:::
:::

@@

::: { #func.calc_day_general_effect.args.train_set .sidebar }
  - **train_set:** Training dataset;

:::
::: { #func.calc_day_general_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
:::

@@

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
:::

@@

Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Date General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Data frame representing the *Date General Effect*;

>>>>

This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below in this section).
:::
:::

@@

::: { #func.calc_day_general_effect.args.train_set .sidebar }
  - **train_set:** Training dataset containing data to compute the *DG Effect*;

:::
::: { #func.calc_day_general_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
:::

@@

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
:::

@@

Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Day General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Data frame representing the *Day General Effect*;
